---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# intermittent

<!-- badges: start -->
![](https://camo.githubusercontent.com/ea6e0ff99602c3563e3dd684abf60b30edceaeef/68747470733a2f2f696d672e736869656c64732e696f2f62616467652f6c6966656379636c652d6578706572696d656e74616c2d6f72616e67652e737667)
<!-- badges: end -->

The goal of intermittent is to assist IR analysts with 'term' data formats originating in various student information systems (SIS). Currently, two origins are supported: SIMS and Campus Solutions.

## Installation

You can install intermittent from GitHub with:

``` r
remotes::install_github("daranzolin/intermittent")
```

## The 'term' class

Create a term object with `term` and indicate an origin.

```{r example}
library(intermittent)
getOption("intermittent.use_terms")
x <- term(2123, origin = "cs")
x
attributes(x)
```

R 'understands' term 2123 to be equivilent of 'Spring 2012'.

```{r error=TRUE}
### Increment the term
x + 1 # To Summer 2012
x + 2 # To Fall 2012
x + 5 # To Fall 2014

x - 1 # To Fall 2011
x - 3 # To Fall 2010

### Comparison
y <- term(2133, "cs")
x < y 
```

Get the academic or calendar year for any term object.

```{r}
acad_year(x)
cal_year(x)
```

Create a sequence of terms with a `seq` method.

```{r}
# Fall 2010 to Spring 2016 with a "sims" origin
sims_terms <- seq(term(20104), 20162)
sims_terms

min(sims_terms)
max(sims_terms)
median(sims_terms) # Retrieve the 'middle' term
```

Use with packages like `dplyr`.

```{r}
library(dplyr)
library(tibble)

tibble(term = c(2123, 2127, 2133, 2137)) %>% 
  mutate(
    term = as_term(term, "cs"),
    year = cal_year(term),
    ay = acad_year(term)
  ) %>% 
  rowwise() %>% 
  mutate(next_term = as.numeric(term + 1)) %>% # rowwise() and as.numeric() to avoid annoying warnings
  ungroup() %>% 
  mutate(next_term = as_term(next_term, "cs"))
```


